A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-29 07_Manuscript.Rmd
Update the order of headings and add page break style for heading 5 to templates

# Manuscript
<!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
<!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->

@@

>>>>

<!-- 
Need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide 
https://www.agronomy.org/publications/journals/author-resources/aj-instructions#headline-article-requirements 
-->
<!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->

## Core ideas
<!-- up to 85 words per idea -->

## Authors - affiliations and email address

##### PAGE BREAK

## Abstract

## Abrebiations

##### PAGE BREAK

@@

## Conclusion

## Supplemental Material
Supplementary material can be found in the following research compendium.
<!-- Insert DOI, perhaps we can render the completed bookdown to PDF to add as the supplementary materials (Paul)-->

## Data Availability
All data and code used in the preparation of this manuscript can be found in the associated research compendium.
<!-- Should we submit the raw data to a data repository like OSF and Figshare? (Paul) -->

## Conflict of Interest Statement
The authors of this paper have no conflicting interest in the research presented in this manuscript
